---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Carlos Henrique"
date: "12/07/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What is expected with the assignment

It is required to create a Shiny application and deploy it on Rstudio's servers. 

The application must include the following:

1. Some form of input (widget: textbox, radio button, checkbox, ...)
2. Some operation on the ui input in sever.R
3. Some reactive output displayed as a result of server calculations
4. You must also include enough documentation so that a novice user could use your application.
5. The documentation should be at the Shiny website itself. Do not post to an external link.

## Brief introduction of my shiny app1

The data set used is "longley" as a supporting material. It gives a macroeconomic data set which provides a well-known example for a highly collinear regression.

```{r longley, echo = TRUE}
plot(longley$GNP, longley$Employed)
```

## Brief introduction of my shiny app2

Based on the simple analysis, we can tell the number of people employed has a linear correlation with the GNP. 
Source: J. W. Longley (1967) *An appraisal of least-squares programs from the point of view of the user*. **Journal of the American Statistical Association 62**, 819–841.

```{r, echo=FALSE}
plot(longley$GNP, longley$Employed)
pred <- lm(longley$Employed ~ longley$GNP)
abline(pred, col = "red")
```

## Brief introduction of my shiny app3

So here's a shiny app to predict the number of people employed by entering the GNP, observed yearly from 1947 to 1962.

You can find my shiny app at : <https://carlos-henrique-campos.shinyapps.io/CourseProject/>

The ui.R and server.R code can be found at : <https://github.com/carloshjr/course9week4>

Thank you!
